### 2024-09-14 Response/Response.tex

We now introduce the detailed network model. Let $\mathcal{D}\triangleq\{1,...,D\}$ denote the set of WDs where $D$ indicates the total number of WDs. Each device $d\in\mathcal{D}$ is connected to the HAP and hence, the cloud server, using a wireless interface. \textcolor{blue}{We regard a complete cycle of executing a single subtask for all WDs having a candidate subtask as an \textit{episode}. Each episode jointly models the harvest-then-offload timing, subtasks' deadlines, and TDMA‌ scheduling of WDs.} As shown in Fig. \ref{fig2}, an episode of length $\Gamma$ is divided into two time frames: WET time (i.e., harvesting time) and offloading/local computation time. In the case of offloading, the latter is consisted of three time slots. The first slot is to relocate the task bits from WD $d\in\mathcal{D}$ to the HAP. Then, the task should be either executed on the MEC server or transmitted to the cloud. We consider that the computation time on the cloud server is negligible due to the high computation capacity compared to WDs or the MEC server. Thus, in the case of offloading to the cloud server, the second time slot indicates the time required to send the task data of WD $d\in\mathcal{D}$ from the HAP to the cloud server and then retrieve the processed data. Finally, the results should be transmitted from the HAP back to the corresponding WD in the third time slot.

\textcolor{blue}{Now that we have introduced the network model, we need to provide an approach to calculate the length of episode $\Gamma$. As stated earlier, each episode reflects the requirements of the harvest-then-offload timing and subtask deadlines. Therefore, $\Gamma$ is directly related to the individual subtask deadlines being executed in that episode. In other words, $\Gamma$ can be calculated as the summation of the subtasks' deadlines. In the next section, we will calculate the length of each episode.}

\begin{table}
	\centering
	\caption{{\color{blue}List of key notations}}
	\ContinuedFloat
	\label{table1}
	{\color{blue}\begin{tabular}{ |p{2cm}|p{12cm}|}
			\hline
			\textbf{Symbol} & \textbf{Description} \\
			\hline
			$x^{\text{L}}_{v_d^u}, x^{\text{M}}_{v_d^u}, x^{\text{C}}_{v_d^u}$ & Binary offloading decisions \\
			$\tau_{1,v_d^u}$ & Length of scheduled time for data transmission of subtask $v_d^u$ \\
			$\tau_{2,v_d^u}$ & Length of scheduled time for execution of subtask $v_d^u$\\
			$\tau_{3,v_d^u}$ & Length of scheduled time for retrieving the result of subtask $v_d^u$ \\
			$\tau_0^u$ & WET time in episode $u$\\
			$p^{u}$ & ET's power in episode $u$ \\
			$\Gamma^u$ & Length of episode $u$ \\
			$\mu_{v_d^u}$ & Response time of cloud server for subtask $v_d^u$ \\
			$C_{v_d^u}$ & Number of CPU cycles required for subtask $v_d^u$ \\
			$N_{i,j}$ & Number of bits required to transmit the result of subtask $i$ and $j$ \\
			$g_d$ & Channel gain between WD $d$ and ET \\
			$h_d$ & Channel gain between WD $d$ and MEC server \\
			$\sigma^2$ & Noise power at the HAP \\
			$\eta_d$ & Energy harvesting efficiency of WD $d$ \\
			$\zeta_{d}$ & CPU's effective switched capacitance of WD $d$ \\
			$r_{t,v_d^u}$ & Virtual resource for tier $t$ and subtask $v_d^u$ \\
			$F^{\text{M},\max}$ & Maximum CPU frequency of MEC server \\
			$F^{\text{L},\max}_{d}$ & Maximum CPU frequency of WD $d$ \\
			$P^{\text{ET},\max}$ & ET's maximum transmission power \\
			$P^{\text{AP},\max}$ & AP's maximum transmission power \\
			$P^{\text{WD},\max}_d$ & Maximum transmission power of WD $d$ \\
			$D$ & Number of WDs \\
			$V_d$ & Number of subtasks of WD $d$ \\
			$B_d$ & Bandwidth of WD $d$ \\
			$\mathcal{D}$, $\mathcal{D}^u$ & Set of WDs \\ 
			$\mathcal{U}$ & Set of episodes \\
			$\mathcal{V}_d$ & Set of subtasks of WD $d$ \\
			$\mathcal{R}^{\text{virt}}$ & Set of virtual resources \\
			$\mathcal{I}_{v_d^u}$ & Set of episodes associated to executing prerequisite subtasks of the subtask $v_d^u$ \\
			$\mathcal{J}_{v_d^u}$ & Set of episodes associated to executing subtasks with the subtask $v_d^u$ as their prerequisite \\
			\hline
	\end{tabular}}
\end{table}

\subsection{Task Model}
Generally, there are two main methods for computation offloading: 1) \textit{Binary offloading}, and 2) \textit{partial offloading} which is also known as \textit{program partitioning} \cite{b4}. \textcolor{blue}{In the former method, each task, as an independent unit, is either fully computed locally or offloaded to an MEC server, based on the system constraints such as task arrival time, deadline, and energy harvesting-related constraints.} However, the latter provides a more fine-grained model of tasks by dividing each of them into a number of interrelated subtasks based on the dependencies inside each task \cite{b4}. These subtasks together form a directed, weighted, and acyclic graph known as \textit{task call graph} \cite{b4}. \textcolor{blue}{The partial offloading provides a more realistic model of tasks as it leverages the task call graph to represent each task. This accurately models the call stack of a computer program\footnote{\textcolor{blue}{For instance, \textit{Pyan}\cite{b41} is a Python module that generates the task call graph of a Python code by analysis of its modules and functions.}}} It can also lead to building networks with a higher performance as the optimal offloading decisions are made for each subtask instead of the whole task. Apart from that, by leveraging program partitioning, one can extract and process them in parallel. That being said, it can be a preferred model for many applications including distributively training deep neural networks \cite{b1}, advanced image processing based on parallel processing, and also most of the augmented reality applications \cite{b12}.

\begin{figure}
	\centering
	\includegraphics[width=180pt]{TDMA.pdf}
	\caption{\textcolor{blue}{Harvest-then-offload scheduling with TDMA protocol for a system of two WDs. An episode of length $\Gamma$ is divided into two times frames of WET and offloading/local computing. In the case of offloading, the offloading/local computing time frame consists of three slots. The first and last slots are for transmitting the data and retrieving the results, respectively. The second slot is dedicated to the computation in the MEC server or transmission to/from the cloud server.}}\label{fig2}
\end{figure}

\begin{figure}
	\centering
	\includegraphics[width=180pt]{task_call_graph.pdf}
	\caption{An example of task call graph with eight subtasks for device $d$. Each parameter $C_{i}$ indicates the computation intensity of subtask $i$ in terms of the number of CPU cycles. Weights $N_{i,j}$ represent the number of bits transferred between subtasks $i$ and $j$.}\label{fig3}
\end{figure}

In this paper, we assume that each device $d\in\mathcal{D}$ has a task which can be partitioned into a number of $V_d$ subtasks using the program partitioning method. We denote $\mathcal{G}_d(\mathcal{V}_d,\mathcal{E}_d)$ as the task call graph of device $d\in\mathcal{D}$ where $\mathcal{V}_d$ indicates the set of vertices which are the subtasks and $\mathcal{E}_d$ denotes the set of edges representing the connection between each two subtasks. Each directed edge $(i,j)\in\mathcal{E}_d$ shows the transmission of the $i$-th subtask output to the $j$-th subtask. An example of this graph with specified computation modes is shown in Fig. \ref{fig3}. For illustration purposes, solid-circled vertices show the subtasks that are computed locally, while vertices with dashed circles correspond to the offloaded subtasks. The black ones are computed on the nearby MEC server and the red one is computed on the remote cloud server. In addition, each subtask $i$ is labeled by a parameter $C_{i}$ which indicates the required CPU cycles to perform the task and represents the task computation intensity. The weight $N_{i,j}$ of the edge from $i$ to $j$ denotes the number of bits required to transmit the result of subtask $i$ to subtask $j$. As the task requires the subtasks to accumulate or send/receive data at the start and end of its procedure, the ones at these ends are executed locally and no offloading decision is made for them \cite{b4}.

\section{Problem Formulation}
This section presents the steps toward formulating the ETEM problem. After providing motivations behind the selection of the objective, we formulate each part of the problem from the objective function to the constraints.

\subsection{Problem Objective}
Due to the high attenuation of RF energy over distances \cite{b8}, WET may require the HAP to consume a considerable amount of energy to provide sustainable operation for WDs. Due to its high cost, it is desired for HAP to consume less energy at the ET. In this paper, we formulate an optimization problem to minimize the total energy consumption of the HAP at the ET by jointly considering computation offloading, scheduling, and power allocation while guaranteeing the task completion and energy constraints. We also adopt the network and task models described in Section II.

Since the proposed WPMEC system consists of multiple WDs and hence multiple task call graphs, we consider the time horizon of the problem to be the number of required episodes to execute the subtasks of all WDs. \textcolor{blue}{We denote $\mathcal{U}\triangleq\{0,...,U-1\}$ as the set of episodes, where $U\triangleq\max_{d\in\mathcal{D}}V_d$  indicates the number of episodes. Note that $V_d$ is obtained from the call graph of the corresponding task.} Therefore, the ET's cumulative energy consumption will be the sum of energy broadcasting over the time horizon. We define $\Gamma^u$, $\tau_0^u$, and $p^u$ as the length of episode $u\in\mathcal{U}$, WET time, and ET's power in episode $u\in\mathcal{U}$, respectively. We will then calculate the HAP's energy consumption at the ET as follows.
\begin{equation}\label{eq2}
	E^{\text{ET}} = \sum_{u\in\mathcal{U}}\tau_0^up^u = \boldsymbol{\tau}_0\boldsymbol{p}^{\intercal},
\end{equation}
where $\boldsymbol{\tau}_0 = \left(\tau_0^u\right)_{u\in\mathcal{U}}$ and $\boldsymbol{p} = \left(p^u\right)_{u\in\mathcal{U}}$ denote the vectors of WET time and ET's transmission power, respectively.

\subsection{Energy harvesting}
In this subsection, we present the energy harvesting-related constraints. \textcolor{blue}{As described earlier, we assume sustainable operation of WDs by only relying on the harvested energy (i.e., battery-less network). Thus, the cumulative energy consumption of the devices on each episode must be no more than their harvested energy.} The required energy of WDs can be divided into two parts: 1) Local computation energy, and 2) energy to send the task's data to the MEC server. We adopt the CPU's dynamic power equation \cite{b2}, \cite{b4}, \cite{b13} to model the local computation energy. We denote $\mathcal{D}^u$ as the set of WDs having a candidate subtask in episode $u\in\mathcal{U}$. We also denote $v_d^u\in\mathcal{V}_d$ as the candidate subtask of WD $d\in\mathcal{D}^u$ to be executed in episode $u\in\mathcal{U}$ and $\tau_{2,v_d^u}$ as the length of time slot scheduled for local computation of this subtask. Therefore, the energy consumption for locally executing subtask $v_d^u\in\mathcal{V}_d$ is
\begin{equation}\label{eq3}
	\begin{aligned}
		E^{\text{LO}}(\tau_{2,v_d^u})=\zeta_d C_{v_d^u}\left(\frac{C_{v_d^u}}{\tau_{2,v_d^u}}\right)^2=\frac{\zeta_d C_{v_d^u}^3}{\left(\tau_{2,v_d^u}\right)^2},&\\
		\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},&
	\end{aligned}
\end{equation}
where $C_{v_d^u}$ is the number of CPU cycles for executing subtask $v_d^u\in\mathcal{V}_d$ of the corresponding task call graph. Moreover, $\zeta_d$ is the CPU's effective switched capacitance \cite{b13} of device $d\in\mathcal{D}^u$.

In order to derive the WD energy consumption in case of offloading, we first use the Shannon formula to calculate the transmission rate between the device and MEC server. Assume that $B_d,g_d,q_{v_d^u},$ and $\sigma^2$ denote the spectrum bandwidth, wireless channel gain of device $d\in\mathcal{D}^u$ for data transmission, transmission power for offloading subtask $v_d^u\in\mathcal{V}_d$, and noise power at the HAP, respectively. The transmission rate is then given as
\begin{equation}\label{eq4}
	r_{v_d^u}=B_d\log_2\left(1+\frac{g_dq_{v_d^u}}{\sigma^2}\right),\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}.
\end{equation}

By utilizing (\ref{eq4}), we will have the following equation for the offloading transmission power.
\begin{equation}\label{eq5}
	q_{v_d^u} = \frac{\sigma^2}{g_d}\left(2^{\frac{r_{v_d^u}}{B_d}}-1\right),\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}.
\end{equation}

According to the task call graph in Fig. \ref{fig3}, the prerequisite of remotely executing a subtask $v_d^u\in\mathcal{V}_d$ for each device $d\in\mathcal{D}^u$ is to offload the required input data (i.e., the summation of weights of the subtask's input edges) to the MEC server. A time slot with length denoted as $\tau_{1,v_d^u}$ is scheduled for data transmission of subtask $v_d^u\in\mathcal{V}_d$ from device $d\in\mathcal{D}^u$ to the MEC server. We consider $\mathcal{I}_{v_d^u}=\{i\in\mathcal{U}|(v_d^i,v_d^u)\in\mathcal{E}_d\}$ as the set of episodes associated to those subtasks which have an output edge to vertex $v_d^u\in\mathcal{V}_d$. Therefore, by utilizing (\ref{eq5}), we can calculate the offloading energy consumption for each subtask $v_d^u\in\mathcal{V}_d$ as follows.
\begin{equation}\label{eq6}
	\begin{aligned}
		E^{\text{OF}}(\tau_{1,v_d^u}) = \tau_{1,v_d^u}q_{v_d^u} = \frac{\tau_{1,v_d^u}\sigma^2}{g_d}\left(2^{\frac{\sum_{i\in\mathcal{I}_{v_d^u}}{N_{v_d^i,v_d^u}}}{\tau_{1,v_d^u}B_d}}-1\right),&\\
		\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U} &.
	\end{aligned}
\end{equation}

We now determine the amount of harvested energy. Let $\eta_d$ and $h_d$ denote the energy harvesting efficiency of WD $d\in\mathcal{D}$ and channel gain between the WD and ET, respectively. The harvested energy during each episode $u\in\mathcal{U}$, denoted as $E^{\text{EH}}(\tau_0^u,p^u)$, is
\begin{equation}\label{eq7}
	E^{\text{EH}}(\tau_0^u,p^u) = \eta_dh_d\tau_0^up^u,\quad\forall u\in\mathcal{U}.
\end{equation}

By denoting $P^{\text{ET}, \max}$ as the maximum power ET can transmit, we will have the following constraint on $p^u$.
\begin{equation}\label{eq7_1}
	0\leq p^u\leq P^{\text{ET}, \max},\quad\forall u\in\mathcal{U}.
\end{equation}

We denote $x^{\text{L}}_{v_d^u}$, $x^{\text{M}}_{v_d^u}$, and $x^{\text{C}}_{v_d^u}$ as binary variables that indicate the offloading decision of subtask $v_d^u$ of device $d\in\mathcal{D}^u$ in episode $u\in\mathcal{U}$. If $x^{\text{L}}_{v_d^u}=1$, the subtask is performed locally while $x^{\text{M}}_{v_d^u}=1$ indicates that the subtask is offloaded to the MEC server and $x^{\text{C}}_{v_d^u}=1$ means that it is offloaded to the cloud server. As stated earlier, we consider that the proposed WPMEC system is fully wireless powered. As a result, the consumed energy of each WD should be at most equal to its harvested energy. Therefore, by utilizing (\ref{eq3}), (\ref{eq6}), and (\ref{eq7}), we have the following constraint.
\begin{equation}\label{eq8}
	\begin{aligned}
		E^{\text{LO}}(\tau_{2,v_d^u})x^{\text{L}}_{v_d^u} + E^{\text{OF}}(\tau_{1,v_d^u})\left(x^{\text{M}}_{v_d^u}+x^{\text{C}}_{v_d^u}\right) \leq E^{\text{EH}}(\tau_0^u,p^u),& \\
		\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}.&
	\end{aligned}
\end{equation}
Note that the excessive harvested energy cannot be stored for future use.

\subsection{Harvest-then-offload TDMA scheduling}
We adopt the harvest-then-offload scheduling mechanism to enable WDs with half-duplex transmission to execute or offload their computation tasks. We also leverage a TDMA protocol for scheduling multiple WDs according to Fig. \ref{fig2}. We consider that an episode of WET and task execution for all WDs should not exceed the length of episode $\Gamma^u$. Therefore, by assuming $u\in\mathcal{U}$ as the episode, the following constraints should be satisfied.
\begin{equation}\label{eq9}
	\tau_0^u + \sum_{d\in\mathcal{D}^u}\left(\tau_{1,v_d^u} +\tau_{2,v_d^u}+\tau_{3,v_d^u}\right) \leq \Gamma^u,\quad\forall u\in\mathcal{U},
\end{equation}
\begin{equation}\label{eq9_1}
	0\leq\tau_0^u\leq\Gamma^u,\quad\forall u\in\mathcal{U},
\end{equation}
where $\tau_{3,v_d^u}$ denotes the length of scheduled time for retrieving the results of subtask $v_d^u\in\mathcal{V}_d$ from the MEC server. \textcolor{blue}{It is worth noting that inequality (\ref{eq9}) also enforces a hard deadline for each cycle of subtasks' execution in each episode. Thus, the total execution time of each task generated by WDs is constrained. This way, we can address the requirements of latency-sensitive tasks as well. Also, it can be concluded that $\Gamma^u$ is a key factor in the optimal value of the ETEM problem. A longer episode (i.e., larger $\Gamma^u$) provides more time for execution of the tasks. In fact, this will enlarge the feasible region of the ETEM optimization problem and enhances the energy-efficiency of the algorithm.}

### 2024-09-14 Response/Response.tex

As illustrated in Fig. \ref{fig2}, in the case of offloading to the MEC server (i.e., $x^{\text{M}}_{v_d^u}=1$) or cloud server (i.e., $x^{\text{C}}_{v_d^u}=1$), the time $\tau_{1,v_d^u}$ must be at most $\Gamma^u$. The figure also shows that if the subtask is executed locally (i.e., $x^{\text{L}}_{v_d^u}=1$ and $x^{\text{M}}_{v_d^u}=x^{\text{C}}_{v_d^u}=0$), $\tau_{1,v_d^u}$ should be equal to zero. Therefore, the following constraint holds.
\begin{equation}\label{eq10}
	\tau^{\min}_{1,v_d^u}\leq\tau_{1,v_d^u}\leq \tau^{\max}_{1,v_d^u},\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},
\end{equation}
where $\tau^{\min}_{1,v_d^u}\triangleq\frac{\sum_{i\in\mathcal{I}_{v_d^u}}N_{v_d^i,v_d^u}}{B_d\log_2\left( 1+\frac{g_dP^{\text{WD}, \max}_d}{\sigma^2}\right)}\left(x^{\text{M}}_{v_d^u} + x^{\text{C}}_{v_d^u}\right)$ and  $\tau^{\max}_{1,v_d^u}\triangleq\Gamma^u\left(x^{\text{M}}_{v_d^u} + x^{\text{C}}_{v_d^u}\right)$ are obtained using (\ref{eq4}). In addition, $P^{\text{WD}, \max}_d$ denotes the maximum transmission power for WD $d\in\mathcal{D}$.

Constraints (\ref{eq8}) and (\ref{eq10}) address a tradeoff between the energy consumption and the transmission duration in the WDs. Above statements are also held for time $\tau_{3,v_d^u}$. Thus, we introduce the following constraint:
\begin{equation}\label{eq11}
	\tau^{\min}_{3,v_d^u} \leq \tau_{3,v_d^u} \leq \tau^{\max}_{3,v_d^u},\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},
\end{equation}
where
$\tau^{\min}_{3,v_d^u}\triangleq\frac{\sum_{j\in\mathcal{J}_{v_d^u}}N_{v_d^u,v_d^j}}{B_d\log_2\left( 1+\frac{g_dP^{\text{AP}, \max}}{\sigma^2}\right)}\left(x^{\text{M}}_{v_d^u} + x^{\text{C}}_{v_d^u}\right), $ $\tau^{\max}_{3,v_d^u}\triangleq\Gamma^u\left(x^{\text{M}}_{v_d^u} + x^{\text{C}}_{v_d^u}\right),$  $\mathcal{J}_{v_d^u}=\{j\in\mathcal{U}|(v_d^u,v_d^j)\in\mathcal{E}_d\},$ and $P^{\text{AP}, \max}$ denotes the maximum AP's transmission power.

It is also worth noting that according to Fig. \ref{fig2}, in the case of local computation, there will not be any time required for data transmission between the MEC server and the corresponding WD. Thus, we have the following constraints for the first and last subtasks of each task call graph.
\begin{equation}\label{eq12_1}
	\tau_{1,v_d^0} = \tau_{3,v_d^0} = \tau_{1,v_d^{V_d-1}} = \tau_{3,v_d^{V_d-1}} = 0,\quad\forall d\in\mathcal{D},
\end{equation}
\begin{equation}\label{eq12_2}
	x^{\text{M}}_{v_d^0} = x^{\text{C}}_{v_d^0} = x^{\text{M}}_{v_d^{V_d-1}} = x^{\text{C}}_{v_d^{V_d-1}} = 0,\quad\forall d\in\mathcal{D},
\end{equation}
where $v_d^0,v_d^{V_d-1}\in\mathcal{V}_d$ indicate the first and last subtasks of device $d\in\mathcal{D}$, respectively.

We denote $F^{\text{L},\max}_{d}$ as the maximum CPU frequency of device $d\in\mathcal{D}$. We also denote $F^{\text{M},\max}$ as the maximum CPU frequency of the MEC server. We consider $C_{v_d^u}$ as the number of CPU cycles for executing a subtask $v_d^u\in\mathcal{V}_d$ on device $d\in\mathcal{D}^u$. Thus, $\tau_{2,v_d^u}$ will be at least $C_{v_d^u}/F^{\text{L},\max}_{d}$ if the subtask is locally computed or $C_{v_d^u}/F^{\text{M},\max}$ in the case of offloading to the MEC server. However, as the cloud servers mostly benefit from powerful processors, we omit the processing delay if the subtask is offloaded to the cloud server. Therefore, the scheduling time $\tau_{2,v_d^u}$ is affected by the server's load and also the round-trip and transmission delay from the MEC server to the cloud. We refer this as the response time which is denoted as $\mu_{v_d^u}\geq 0$ for each device $d\in\mathcal{D}^u$ and episode $u\in\mathcal{U}$. As a result, we have
\begin{equation}\label{eq13}
	\tau^{\min}_{2,v_d^u} \leq \tau_{2,v_d^u} \leq\Gamma^u,\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U},
\end{equation}
where $\tau^{\min}_{2,v_d^u}\triangleq\frac{C_{v_d^u}}{F^{\text{L},\max}_{d}}x^{\text{L}}_{v_d^u} + \frac{C_{v_d^u}}{F^{\text{M},\max}}x^{\text{M}}_{v_d^u} +
\mu_{v_d^u}x^{\text{C}}_{v_d^u}$. The response time $\mu_{v_d^u}$ is estimated by the MEC server at the beginning of each episode $u\in\mathcal{U}$ for each WD $d\in\mathcal{D}^u$.

\subsection{ET's Energy Minimization (ETEM) Problem}
To formulate the problem, we first define three offloading decision vectors for cloud, edge, and local computation as $\boldsymbol{x}^\text{C} = \left(x^{\text{C}}_{v_d^u}\right)_{\sum_{d\in\mathcal{D}}V_d}$, $\boldsymbol{x}^{\text{M}} = \left(x^{\text{M}}_{v_d^u}\right)_{\sum_{d\in\mathcal{D}}V_d}$, and $\boldsymbol{x}^{\text{L}} = \left(x^{\text{L}}_{v_d^u}\right)_{\sum_{d\in\mathcal{D}}V_d}$, respectively. We also define decision matrix $\boldsymbol{X} = \left(x_{t,v_d^u}\right)_{3\times \sum_{d\in\mathcal{D}}V_d} = \left(\boldsymbol{x^\text{C}};\boldsymbol{x^\text{M}};\boldsymbol{x^\text{L}}\right)$, where each row corresponds to a tier number $t\in\{1,2,3\}$. We also define $\boldsymbol{T} = (\tau_{m,v_d^u})_{3\times \sum_{d\in\mathcal{D}}V_d}$ as the computation scheduling matrix with $m\in\{1,2,3\}$ representing the time frame number. We can now formulate the ETEM problem as follows.
\begin{subequations}
	\begin{alignat}{4}
		\text{ETEM: }\displaystyle{\minimize_{\boldsymbol{X},\boldsymbol{p},\boldsymbol{\tau}_0,\boldsymbol{T}}}\quad & \boldsymbol{\tau}_0\boldsymbol{p}^{\intercal} \label{p1a}\\
		%
		\textrm{subject to} \quad & \text{constraints } (\ref{eq7_1})\text{--}(\ref{eq13}), \label{p1b}\\
		%
		\begin{split}
			&x^{\text{L}}_{v_d^u} + x^{\text{M}}_{v_d^u} + x^{\text{C}}_{v_d^u} = 1,\\
			%
			&\quad\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}, \label{p1c}
			%
		\end{split}\\
		\begin{split}
			&x^{\text{L}}_{v_d^u}, x^{\text{M}}_{v_d^u}, x^{\text{C}}_{v_d^u}\in\left\{0,1\right\},\\
			%
			&\quad\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}. \label{p1d}
			%
		\end{split}
	\end{alignat}
\end{subequations}

ETEM is a mixed-integer optimization problem which is intractable. In the next section, we will propose our algorithm called WiEnTM to efficiently solve the problem by leveraging bipartite graph matching and parallel processing\cite{b16}.

\section{Wireless Energy Transmission Minimization (WiEnTM) Algorithm}

In this section, we propose our parallel WiEnTM algorithm to solve the ETEM problem using bipartite graph matching. We also analyze the time complexity of each parallel block of the algorithm.

\subsection{Bipartite Graph Matching}
Matching in graph theory can provide a tractable approach to combinatorial optimization problems \cite{b17}. Matching theory has been widely used for resource allocation in wireless networks where the users and resources are modeled as a bipartite graph \cite{b16}, \cite{b17}. In this graph, users are connected to resources via edges. Each edge is associated with a weight which represents the cost of using the corresponding resource. A subset of edges associated with a feasible resource allocation is called a \textit{matching}. The goal is to find the minimum weighted graph matching.

\begin{figure*}[ht]
	\centering
	\begin{subfigure}{.21\textwidth}
		\centering
		\includegraphics[height=\linewidth]{matching1.pdf}
		\caption{}
		\label{fig:4a}
	\end{subfigure}\hspace{8mm}
	\begin{subfigure}{.21\textwidth}
		\centering
		\includegraphics[height=\linewidth]{matching2.pdf}
		\caption{}
		\label{fig:4b}
	\end{subfigure}

	\caption{An example for matching bipartite graph of subtasks $\mathcal{V}_d$ and computation resources $\mathcal{R}$. Set $\mathcal{R}$ contains resources $r_1$ (i.e., cloud servers), $r_2$ (i.e., MEC servers), and $r_3$ (i.e., local devices). a) Many-to-one matching. b) Equivalent one-to-one matching by utilizing virtual resources $\mathcal{R}^{\text{virt}}$ where each $r_{t,v_d^u}$ is related to tier number $t\in\{1,2,3\}$ and subtask $v_d^u$.} \label{fig:4}
\end{figure*}

The bipartite graph in Fig. \ref{fig:4} provides an example of matching problem in the proposed WPMEC system. In Fig. \ref{fig:4a}, each subtask $v_d^u\in\mathcal{V}_d$ of device $d\in\mathcal{D}^u$ in episode $u\in\mathcal{U}$ is matched with computation resources of set $\mathcal{R}$ which consists of cloud, MEC server, and local devices. It is important to note that device $d$ can only be matched with itself or cloud/edge resources not other devices.

\textcolor{blue}{To leverage the matching algorithm, we need to calculate the cost of each matching between subtasks and computing resources. To accomplish this, we first transform the ETEM problem into an equivalent simplified problem. We then show that the transformed problem is decomposable, and the resultant decomposed problems are still equivalent to the ETEM problem.}

For each matching, the binary decision variables $x_{v_d^u}^{\text{L}}$, $x_{v_d^u}^{\text{M}}$, and $x_{v_d^u}^{\text{C}}$ will have known values (e.g., matching subtask $v_d^u\in\mathcal{V}_d$ with the cloud resource will result in $x_{v_d^u}^{\text{C}} = 1$ and $x_{v_d^u}^{\text{L}}=x_{v_d^u}^{\text{M}}=0$). However, the ETEM problem is still non-convex even with eliminating binary variables. This is due to the term $\tau_0^up^u$ which is neither a convex nor concave function of $\tau_0^u$ and $p^u$. For the sake of resolving this issue, we present the following theorem.

\begin{theorem}
	Given a matching (i.e., particular values of binary variables $x^{\text{L}}_{v_d^u}$, $x^{\text{M}}_{v_d^u}$, and $x^{\text{C}}_{v_d^u}$), ETEM can be transformed into a convex optimization problem.
\end{theorem}
\begin{IEEEproof}
	Refer to Appendix A.
\end{IEEEproof}

We now transform the ETEM problem with the change of variable $\varepsilon^u=\tau_0^up^u$ into a more tractable form. This helps us calculate the edge weights in the matching graph. In order to accomplish this, it is required to decompose the aforementioned problem into problems for each subtask $v_d^u\in\mathcal{V}_d$ of device $d\in\mathcal{D}$ in episode $u\in\mathcal{U}$. We first provide two important remarks as follows.

\begin{remark}
	The optimal value of variable $\tau_{3,v_d^u}$ will be
	\begin{equation}\label{eq18}
		\tau_{3,v_d^u}^{\ast} \triangleq \tau_{3,v_d^u}^{\min},\quad\forall d\in\mathcal{D}^u, \forall u\in\mathcal{U}.
	\end{equation}
\end{remark}
\noindent The above equation eliminates constraint (\ref{eq11}).

Variable $\tau_{3,v_d^u}$ is only present in constraints (\ref{eq9}) and (\ref{eq11}). Since (\ref{eq9}) forces a hard deadline on the scheduling times, it is desirable for $\tau_{3,v_d^u}$ to have the smallest possible value which is dictated by constraint (\ref{eq11}). Therefore, at the optimal point of ETEM problem, \ref{eq18} will be achieved.

\begin{remark}
	We can calculate the transmitted wireless energy during each episode $u\in\mathcal{U}$ as
	\begin{equation}\label{eq19}
		\varepsilon^u = \max_{d\in\mathcal{D}^u}\left\{\frac{E^{\text{LO}}(\tau_{2,v_d^u})x^{\text{L}}_{v_d^u}}{\eta_d h_d} + \frac{E^{\text{OF}}(\tau_{1,v_d^u})\left(x^{\text{M}}_{v_d^u}+x^{\text{C}}_{v_d^u}\right)}{\eta_d h_d}\right\},
	\end{equation}
	where $v_d^u\in\mathcal{V}_d$ is the candidate subtask of device $d\in\mathcal{D}^u$ that is being executed in episode $u\in\mathcal{U}$.
\end{remark}

We know that the objective of the ETEM problem is to minimize the wireless energy transmission. This minimum value must meet the energy requirements of all WDs. Therefore, it is the maximum energy consumption among WDs in each episode $u\in\mathcal{U}$. Using the above remark, we can rewrite the objective function and eliminate constraint (\ref{eq8}).

Using (\ref{eq19}), we can transform ETEM into a minimax optimization problem but it may still be difficult to solve when there are large number of WDs. We know that constraint (\ref{eq9}) is creating a dependency between subtasks. By rewriting this constraint for each subtask, we will be able to reduce this minimax optimization problem into a number of independent problems. As a result, the ETEM problem will convert into a minisum optimization problem \cite{b18} which is easier to solve.

In order to eliminate the aforementioned dependency in constraint (\ref{eq9}), we first consider a given value for the WET time $\tau_0^u$ which satisfies constraint (\ref{eq9_1}). Thus, the ET's transmitted energy will only depend on $p^u$. There are iterative methods to calculate the appropriate value of $\tau_0^u$ such as the one proposed in \cite{b2}. By decomposing the summation on the left-hand side of (\ref{eq9}), this constraint can be rewritten for each subtask $v_d^u\in\mathcal{V}_d$. We first introduce a new parameter $0\leq\beta_{v_d^u}\leq|\mathcal{D}^u|$ which reflects the priority, computation complexity, or input/output size of each subtask $v_d^u\in\mathcal{V}_d$. We then introduce the following constraint.
\begin{equation}\label{eq28}
	\tau_{1,v_d^u} + \tau_{2,v_d^u} \leq \frac{\beta_{v_d^u}}{|\mathcal{D}^u|}\left(\Gamma^u-\tau_0^u\right) - \tau_{3,v_d^u}^{\ast}.
\end{equation}

We now reconstruct (\ref{eq9}) using (\ref{eq28}). To do so, we accumulate each side of (\ref{eq28}) over all WDs in $\mathcal{D}$ and choose $\beta_{v_d^u}$ such that
\begin{equation}\label{eq27}
	\sum_{d\in\mathcal{D}^u}\beta_{v_d^u} \leq 	|\mathcal{D}^u|,\quad\forall u\in\mathcal{U}.
\end{equation}

It can be easily shown that when the above condition holds, constraint (\ref{eq28}) ensures that constraint (\ref{eq9}) is met. Moreover, in the case of equality, constraints (\ref{eq9}) and (\ref{eq28}) will be equivalent. \textcolor{blue}{We will analyze the effect of $\beta_{v_d^u}$ on the optimal solution in Section V.}

For ease of exposition, we now define the following two functions for each $v_d^u\in\mathcal{V}_d$ assuming $x^{\text{L}}_{v_d^u}$, $x^{\text{M}}_{v_d^u}$, and $x^{\text{C}}_{v_d^u}$ are given.
\begin{equation}\label{eq20}
	\begin{aligned}
		e_1(\tau_{1,v_d^u}) &\triangleq \frac{E^{\text{OF}}_{v_d^u}\left(x^{\text{M}}_{v_d^u}+x^{\text{C}}_{v_d^u}\right)}{\eta_d h_d}\\
		&= \frac{\tau_{1,v_d^u}\left(x^{\text{M}}_{v_d^u}+x^{\text{C}}_{v_d^u}\right)}{\sigma^{-2}g_d\eta_d h_d}\left(2^{\frac{\sum_{i\in\mathcal{I}_{v_d^u}}{N_{v_d^i,v_d^u}}}{\tau_{1,v_d^u}B_d}}-1\right),
	\end{aligned}
\end{equation}
\begin{equation}\label{eq21}
	e_2(\tau_{2,v_d^u}) \triangleq \frac{E^{\text{LO}}_{v_d}x_{\text{L}}^{v_d}}{\eta_d h_d} = \frac{\zeta_d C_{v_d^u}^3x^{\text{L}}_{v_d^u}}{\eta_d h_d\left(\tau_{2,v_d^u}\right)^2}.
\end{equation}
